% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Kevin D. Duncan}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}


% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\sffamily\mdseries\Large}
\subsectionfont{\sffamily\mdseries\itshape\large}

\usepackage{enumitem}

\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\newcommand{\degree}[3]{#1,\ #2\quad#3\par}

\setlist[itemize]{leftmargin=*}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{\linewidth}
  \begin{tabular}{llllll}
    Phone: & (978) 390-3459 & 
    Email: & \href{mailto:kdduncan@iastate.edu}{\tt kdduncan@iastate.edu} & 
    Homepage: & \href{kdduncan.github.io/}{\tt kdduncan.github.io/} \\
  \end{tabular}
\end{minipage}

\section*{Qualifications Summary}

Economics PhD with research in econometric theory and applied microeconomics. Experience implementing both tall and wide data driven projects in R and Stata. Advanced knowledge of statistical theory and implementation of machine learning techniques.

\section*{Education}

\begin{tabular}{@{}llll}
(Expected) Dec. 2019  & Ph.D. &Economics &Iowa State University \\
2015 & M.S. &Economics &Iowa State University \\
2011 & B.S. &Economics \& Public Policy &The George Washington University
\end{tabular}


\section*{Experience}
\begin{itemize}
\item Estimated the impact of the troubled asset relief program on business dynamics using bank call sheet data, requiring regularized regression for variable selection over hundreds of available covariates. 
\item Developed joint hypothesis tests for panel data with serially correlated errors with large numbers of inconsistent parameter estimation relative to the sample size.
\item Utilized R and Stata to construct estimators and carry out large data driven projects that included both many observations or covariates.
\item Forecasted local economic growth using state climate business indices. Responded to reviewer comments and generate published peer reviewed work.
\end{itemize}

\section*{Publications \& Working Papers}

\begin{itemize}
\item ``Do State Business Climate Indicators Explain Relative Economic Growth at State Borders?'' \textit{with Georgeanne Artz, Peter Orazem, and Arthur Hall}, Journal of Regional Science, Vol. 56, No. 3, 2016, pp. 395-419
\item ``The Troubled Asset Relief Program's Effect on Firm Entry over the Business Cycle''
\item ``Linear Hypothesis Tests over Fixed Effects with Serially Correlated Panels''
\item ``Impact of Taxes on Firm Location Along State Borders,'' \textit{with Georgeanne Artz and Peter Orazem}
\end{itemize}

\section*{Teaching \& Presentations}
\begin{tabular}{@{}llll}
2018 & Adjunct Instructor & Des Moines Area Community College & Ankeny IA \\
\end{tabular}
\begin{itemize}
\item 2019 Midwest Economics Association, 2016 Midwest Economics Association, 2015 Southern Economics Association, Missouri Valley Economics Association, 2014 Midwest Economics Association
\end{itemize}

\end{document}