% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Kevin D. Duncan}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=0.5in,
  right=0.5in,
  top=0.5in,
  bottom = 0.5in
}


% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\sffamily\mdseries\Large}
\subsectionfont{\sffamily\mdseries\itshape\large}

\usepackage{enumitem}

\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

\renewcommand\labelenumi{}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}


\newcommand{\degree}[3]{#1,\ #2\quad#3\par}

\setlist[itemize]{leftmargin=*}

\begin{document}

% Place name at left
{\huge \name} \makebox[.65\textwidth][r]{\begin{minipage}{0.45\textwidth}
  \begin{tabular}{ll} \\
    Phone: & (XXX) XXX-XXXX\\
    Email: & \href{mailto:XXXX@fhfa.gov}{\tt XXXX@XXXX.xxx} \\
    Last updated: & March 2014 \\
  \end{tabular}
\end{minipage}}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.0in}

%\begin{minipage}{0.45\linewidth}
%  \href{http://www.unc.edu/}{Iowa State University} \\
%  Department of Economics \\
%  Heady Hall \\
%  Ames IA, 50014
%\end{minipage}


\section*{Education}

\begin{tabular}{@{}llll}
    2014 & MSc & Economics &Iowa State University \\
  2011 & BSc & Economics \& Political Science & The George Washington University
\end{tabular}

\section*{Employment}

\begin{tabular}{@{}llll}
  Spring 2012 & Adjunct Fellow & Tax Foundation \\
  Summer-Fall 2011 & Summer Intern & Koch Institute \& GWU Regulatory Studies Center \\
\end{tabular}


\section*{Quantitative Experience}
\subsection*{Analytical Skillset}
\begin{itemize}
\item Strong mathematical background: completed coursework in real analysis I-II, linear algebra, and differential equations. 
\item Nominated by my professors to be upgraded into the PhD in Economics program starting Fall 2013 for exemplary performance in MSc program.
\item Evaluated the impacts of 9 top marginal tax rates on establishment entry, exit, employment expansion, and employment contraction from 2000 to 2016 using a border-difference estimator in Stata (Master's thesis).
\end{itemize}
\subsection*{Technical Skillset}
\begin{itemize}
\item Currently engaged in masters level coursework in economics courses, and advanced undergraduate mathematics and computer science courses. Exposure and experience using Stata, R, Java, and ArcGIS. 
\item Training in masters level econometrics and mathematical statistics courses.
\item Published an article evaluating the forecast performance of state level business climate indices as published by think tanks and professional organizations on future county and state level growth using a border-difference estimator.
\item Linked DC Liquor licenses to relevant regulatory district in ArcGIS, estimated a model of liquor licensings being put in place using a panel Probit model. Further estimated the impacts of local characteristics on total liquor licenses accounting for Heckman selection in a local hold being in place.
\end{itemize}
\subsection*{Communications Skillset}
\begin{itemize}
\item Experience presenting to undergraduate students as a teaching assistant.
\item Invited presentation on the economics of sorting for advanced course on economic discrimination, including sorting models programmed in Java and NetLogo.
\item Experience presenting ongoing research to both peer stake holders in economic conferences, as well as policy and stakeholder levels via experience interning at think tanks.
\item Wrote blog posts and opinion editorials published online at nationally recognized outlets.
\end{itemize}

\section*{Other Experience}
\begin{itemize}
\item Omicron Delta Epsilon honors, department tutor for the GWU Department of Economics, including calculus intensive microeconomics and macroeconomics, and econometrics.
\item Iowa State University Department of Economics Computer Committee. Wrote \$25,000 grant to improve student server cluster that was approved in a competitive merit based application pool.
\end{itemize}

\end{document}
