% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{comment}
% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Kevin D. Duncan}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}


% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\sffamily\mdseries\Large}
\subsectionfont{\sffamily\mdseries\itshape\large}

\usepackage{enumitem}

\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

\renewcommand\labelenumi{}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}


\newcommand{\degree}[3]{#1,\ #2\quad#3\par}

\setlist[itemize]{leftmargin=*}

\begin{document}

% Place name at left
{\huge \name} \makebox[.65\textwidth][r]{\begin{minipage}{0.45\textwidth}
  \begin{tabular}{ll} \\
    Phone: & (978) 390-3459 \\
    Email: & \href{mailto:kevindduncan@gmail.com}{\tt kevindduncan@gmail.com} \\
    Homepage: & \href{kdduncan.github.io/}{\tt kdduncan.github.io/} \\
    Last updated: & \today \\
  \end{tabular}
\end{minipage}}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

%\begin{minipage}{0.45\linewidth}
%  \href{http://www.unc.edu/}{Iowa State University} \\
%  Department of Economics \\
%  Heady Hall \\
%  Ames IA, 50014
%\end{minipage}


\section*{Education}

\begin{tabular}{@{}llll}
  2020  & Ph.D. & Economics &Iowa State University \\
    2015 &M.Sc. & Economics &Iowa State University \\
  2011 & B.Sc. & Economics \& Political Science & The George Washington University
\end{tabular}

\section*{Professional Experience}

Senior Economist, Credit \& Collateral Risk Modeling Branch, Federal Housing Finance Agency, Sep. 2021 - \textit{current}

\begin{itemize}
\item Led examination of FHLBank collateral and securities valuation and haircut models, unsecured counterparty models, and member credit risk models, including credit union, bank, and insurance company probability of default models.
\item Issued technical findings for improvement in FHLBank credit and collateral models, model risk management, and policies and procedures.
\item Conducted research into Value-at-Risk (VaR) estimation techniques. Issued report on technical issues in time series and panel data estimation of VaR and estimation method comparisons and issues with simulation code in R. Carried out simulated portfolios in polypaths subject to market risk and HPI shocks against reduced form estimates of VaR.
\item Spearheaded the overhaul of a quarterly member credit report requiring SQL and Stata integration.
\item Ongoing research into the use of state-space methods to estimate VaR and Expected Shortfall using Bayesian methods in Stan.
\end{itemize}

Economist, Credit \& Collateral Risk Modeling Branch, Federal Housing Finance Agency, July 2020 - Aug. 2021


\section*{Research}

\subsection*{Journal Articles}

\begin{itemize}
\item ``How Relative Marginal Tax Rates Affect Establishment Entry at State Borders'' \textit{with Yulong Chen, Liyuan Ma, and Peter Orazem}, Forthcoming at Small Business Economics. (Previously circulated as ``Impact of Taxes on Firm Location Along State Borders,'' \textit{with Georgeanne Artz (\dag) and Peter Orazem})
\item``Do State Business Climate Indicators Explain Relative Economic Growth at State Borders?'' \textit{with Georgeanne Artz, Peter Orazem, and Arthur Hall}, Journal of Regional Science, Vol. 56, No. 3, 2016, pp. 395-419
\end{itemize}

\subsection*{Working Papers}

\begin{itemize}
\item ``Do Nudges Induce Safe Driving? Evidence from Dynamic Message Signs'' \textit{with Sher Afghan Asad}
\item ``The Capital Purchase Program's Effect on Firm Entry over the Business Cycle''
\item ``Linear Hypothesis Tests over Fixed Effects with Serially Correlated Panels''

\subsection*{Work in Progress}
\item ``Conditional Value at Risk Models with Mixed Frequency Data: A State Space Approach'' \textit{with Brice Green}
\item ``FHLBank System in Perspective''
\end{itemize}




\section*{Grants \& Awards}


\begin{itemize}
\item 2015 Wayne W. Gross Graduate Fellowship
\item 2015 \textit{ with Oleksandr Zhylyevskyy, Christopher Jorgensen, and Michael Long}, ''Graduate Student Server Upgrades in Heady Hall,'' Iowa State University College of Liberal Arts and Sciences Computation Advisory Committee Grant (\$25,908.92)
\end{itemize}
\section*{Conference Presentations \& Invited Talks}


\begin{itemize}
\item 2022 Urban Economics Association North American Meetings
\item 2021 ITEA Annual Conference and School on Transportation Economics
\item 2020 North American Meetings of the Regional Science Association, Federal Housing Finance Agency, Census Bureau's Center for Economic Studies, Southern Regional Science Association (canceled due to COVID)
\item 2014-2019 Midwest Economics Association x3, Southern Economics Association, Missouri Valley Economics Association
\end{itemize}

\section*{University and Department Service}

\begin{itemize}
\item 2014 - 2017 (non continuously) Graduate Student Seminar Coordinator, ISU Graduate College Peer Mentor, Economics Department Computer Committee
\end{itemize}

\section*{Teaching Experience}


\begin{tabular}{@{}llll}
2018 & Adjunct Instructor & Des Moines Area Community College & Ankeny IA \\
2012-2015 & Teaching Assistant & Iowa State University & Ames IA \\
\end{tabular}




\end{document}
